Two applications of logic programming to Coq

### 2020-11-09 papers/types2020/preamble.tex
progress on 4
sec 4 ready some work on conclusion
related work bits spear thru the paper
ported the appendix and sec3 to kernel-v2

sec3 is still a mess
ACM Category
commenti di Enrico

\Copyright{M. Manighetti, D. Miller, and A. Momigliano}
%TODO mandatory, please use full first names. LIPIcs license is
%"CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} 
%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Proof assistant, logic programming, Coq, \lP}
%TODO mandatory; please add comma-separated list of keywords

@@

\nolinenumbers %uncomment to disable line numbering

@@

>>>>

\Copyright{M. Manighetti, D. Miller and A. Momigliano}
%TODO mandatory, please use full first names. LIPIcs license is
%"CC-BY";  http://creativecommons.org/licenses/by/3.0/

\ccsdesc[500]{Theory of computation~Logic and verification}
%TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

\keywords{Proof assistants, logic programming, Coq, \lP, property-based testing}
%TODO mandatory; please add comma-separated list of keywords

@@

 \acknowledgements{Thanks to Enrico Tassi for his help with Coq-Elpi and his comments on the paper.}
\nolinenumbers %uncomment to disable line numbering

@@

% LocalWords:  Matteo Manighetti Inria

### 2020-11-09 papers/types2020/sec3.tex
commenti di Enrico

The \lsti{dprolog} tactic can be seen as a programmable version of
Coq's \lsti{auto}: it currently lacks the latter's capability of
solving goals by \lsti{reflexivity} as well as the modularity of using
\lsti{Hints} as introduction rules; on the bright side, it is not
restricted to depth-first search, since it follows the dictate of the
given FPC, for example adding iterative-deepening search. Furthermore, the FPC can
provide a \emph{trace} that may be more customized than the one
offered by the \lsti{auto}'s hard-wired \lsti{Debug} facility.

@@

% LocalWords:  backchaining disjunct LJT dep qheight qsize orE someE
% LocalWords:  Elpi modularity Herbelin bc PTSC's dprolog CIC init lp
% LocalWords:  Andreoli's basicstyle lprolog sigs Coq's sortedness Ev
% LocalWords:  backchain gref indt indc coq dest unfoldings str fpc
% LocalWords:  evar nat forall ys elpi Qed lc args ljf HOAS unfoldE
% LocalWords:  FPCs Prolog evars untyped decideE

>>>>

The \lsti{dprolog} tactic can be seen as a programmable (and possibly
faster) version of Coq's \lsti{eauto}, although it currently lacks the
latter's capability of solving goals by
\lsti{reflexivity}; % as well as the modularity of using
% \lsti{Hints} as introduction rules
 \lsti{dprolog} is not restricted to depth-first search, since
it follows the dictate of the given FPC, for example we could easily add
iterative-deepening search. Furthermore, the tactic can still use
\lsti{Hints} via Elpi's \lsti{Db} feature, and FPCs can provide a
\emph{trace} that may be more customizable than the one offered by the
\lsti{(e)auto}'s hard-wired \lsti{Debug} facility.

@@

% LocalWords:  backchaining disjunct LJT dep qheight qsize orE someE
% LocalWords:  Elpi modularity Herbelin bc PTSC's dprolog CIC init lp
% LocalWords:  Andreoli's basicstyle lprolog sigs Coq's sortedness Ev
% LocalWords:  backchain gref indt indc coq dest unfoldings str fpc
% LocalWords:  evar nat forall ys elpi Qed lc args ljf HOAS unfoldE
% LocalWords:  FPCs Prolog evars untyped decideE eauto
